### 2020-03-24 paper/conclusion.tex
after Prof. Huff's comments

\section{Conclusion} \label{Conclusion}
In the current work, we introduced design of a reactivity control system for the 
Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR). The 
design has been evaluated at the startup for the full-core geometry using 
SERPENT-2 Monte-Carlo code. We considered three various startup compositions of 
the fuel salt: (1) $^{232}$Th as fertile and $^{233}$U as fissile material; 
(2) $^{232}$Th and Pu, extracted from \gls{LWR} \gls{SNF}; (3) 
$^{232}$Th and TRU vector, extracted from \gls{LWR} \gls{SNF}.

@@

\section{Future work}
In Part II of this research effort, we will evaluate the effect of fuel salt 
burnup on the CRW. The depleted fuel composition will be obtained using a
SERPENT-2 online reprocessing subroutine \cite{aufiero2013extended} and 
batch-wise tool SaltProc \cite{rykhlevskii_arfc/saltproc_2018, 
rykhlevskii_milestone_2019}. Additionally, the authors intend to investigate 
kinetic parameters' (effective delayed neutron fraction $\beta_{eff}$ and 
effective delayed neutron precursor decay constant $\lambda_{eff}$) evolution 
during the SD-TMSR operation. These parameters are crucial for accident 
transient analysis, which will be performed using Moltres 
\cite{lindsay_introduction_2018}, multi-physics code for liquid-fueled MSR 
simulation with taking into account the neutron precursors drift.

>>>>

\section{Conclusion} \label{Conclusion}
In the current work, we proposed a reactivity control system design for the 
Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR). The 
design has been evaluated at the startup for the full-core geometry using the
SERPENT-2 Monte-Carlo code. We considered three startup fuel salt compositions of 
the fuel salt: (1) $^{232}$Th as fertile and $^{233}$U as fissile material; 
(2) $^{232}$Th and Pu, extracted from \gls{LWR} \gls{SNF}; (3) 
$^{232}$Th and TRU, extracted from \gls{LWR} \gls{SNF}.

@@

\section{Future work}
In Part II of this research effort, we will evaluate the effect of fuel salt 
burnup on the CRW. The depleted fuel composition will be obtained using a
SERPENT-2 online reprocessing subroutine \cite{aufiero2013extended} and 
batch-wise tool SaltProc \cite{rykhlevskii_arfc/saltproc_2018, 
rykhlevskii_milestone_2019}. Additionally, the authors intend to investigate 
kinetic parameters' (effective delayed neutron fraction $\beta_{eff}$ and 
effective delayed neutron precursor decay constant $\lambda_{eff}$) evolution 
during the SD-TMSR operation. These parameters are crucial for accident 
transient analysis, which will be performed using Moltres 
\cite{lindsay_introduction_2018}, a multi-physics application for liquid-fueled MSR 
simulation which takes into account the neutron precursors drift.

### 2020-03-24 paper/introduction.tex
after Prof. Huff's comments

The \gls{GIF} \cite{doe2002technology} determined six innovative reactor 
systems: the Very High-Temperature Reactor (VHTR), the \gls{MSR}, the 
Supercritical Water-Cooled Reactor (SWCR), the Gas-cooled Fast Reactor (GFR), 
the Sodium-cooled Fast Reactor (SFR), and the Lead-cooled Fast Reactor (LFR). 
The MSR is the only liquid-fueled reactor among these reactors. Major nuclear 
centers pursue MSRs with renewed interest \cite{betzler_impacts_2019, 
ashraf2020whole,betzler2016modeling,mohsin2019safety,zhang2020radiotoxicity}.
The MSR is a promising technology because of its dynamics, especially for 
thorium fuel utilization. However, this technology has difficulties in safety, 
online reprocessing, and fuel handling. Safety is one of the primary goals of 
the MSR system, which was understudied and requires further investigation. The 
unique characteristics of the MSR (liquid fuel, flux level, neutron economy, 
etc.) strongly affect its control system design. Graphite-moderated MSRs have 
a negative total temperature coefficient of reactivity 
\cite{ashraf2020whole,robertson_conceptual_1971,nuttin2005potential,rykhlevskii2019modeling,li_optimization_2018}.
Doppler effect and thermal expansion of the fuel reduce core reactivity when 
the core heats up. MSR designs have drain tanks to 
hold and cool down the liquid fuel in an emergency case. A freeze plug, which 
is located under the core, passively melts when the fuel temperature reaches a 
critical point, and drains the fuel salt from the reactor vessel to the drain 
tanks. The drain tanks have a subcritical
configuration with a large free 
surface area to readily dissipate heat by passive cooling 
\cite{elsheikh2013safety}.

At the Beginning of Life (BOL), the MSR is commonly loaded with a larger amount of 
fuel than that required to achieve criticality (necessary for long-term core 
operation); this leads to excess reactivity at the BOL. Recent studies on MSRs showed that this excess reactivity 
at the BOL is large for many refueling scenarios 
\cite{ashraf2020Strategies,ashraf2020whole,rykhlevskii2019modeling,betzler2016modeling,ashraf2018nuclear,ashraf2019modeling}.
Additionally, during burnup, the online 
reprocessing and refueling leads to slow reactivity change, which 
should be compensated \cite{ashraf2020Strategies,ashraf2020whole}. 
The online reprocessing and refueling system helps to control the reactivity of 
the MSRs \cite{ashraf2020whole,ashraf2019Preliminary}. However, the most common and reliable procedure 
to control the reactor is to insert or withdraw control rods made of material 
with a large neutron absorption cross section (e.g., boron, cadmium) 
\cite{duderstadt650nuclear}. 
Insertion of control rods introduces an amount of negative reactivity into the 
core. This negative reactivity helps to compensate the excess reactivity and 
adjust the power level of the core or shut down the reactor in case of 
emergency \cite{glasstone1967nuclear}. Therefore, we should estimate 
the reactivity worth of the control rods 
\cite{varvayanni2009estimation,fadaei2009control,aoyama2007core,bretscher1997computing}.
 The reactivity worth of control rods correlates with the interference 
(shadowing effects) between control rod clusters 
\cite{girardin2008development,vcerba2017optimization}. 
The control rod worth and its efficiency to absorb excess positive reactivity is a subject of major interest since it directly affects reactor safety \cite{liu2018criticality,atkinson2019small,vcerba2017optimization,do2019criticality,guo2019advanced,varvayanni2009estimation}.

Boron carbide (B$_4$C) is a commonly used material for the control rods 
\cite{zhong2019preliminary,steinbruck2010degradation,dunner1984absorber}; 
however, we may need to enrich the boron isotope ($^{10}$B) to reach 
the necessary absorption cross section. Additionally, issues related to helium gas release through (n,$\alpha$) reactions of $^{10}$B, high loss of the reactivity worth, and swelling limit the B$_4$C lifespan 
\cite{guo2019optimized}. Guo (2019), Gosset (2017), and Rudy (2011) summarized the properties of the 
potential alternative absorbers for Generation-IV reactors such as 
hafnium-based materials and rare earth element oxides. These absorbers have 
high thermal conductivity, good resistance to neutron irradiation, and
almost no gas release (absorbing neutrons mainly through (n,$\gamma$) reactions)
\cite{guo2019optimized,gosset2017absorber,konings2011comprehensive}.

The \gls{SD-TMSR} with a thermal power of 2,250 MW$_{th}$ 
\cite{ashraf2020whole,li_optimization_2018} is a graphite-moderated 
molten salt reactor. Adjusting fertile and fissile feed rates helps to control the reactivity of 
the SD-TMSR \cite{ashraf2020whole,ashraf2020Strategies,li_optimization_2018}. However, a reactivity control system for maneuvering and emergency shutdown has not been introduced in literature \cite{li_optimization_2018,zou2018transition,zhang2020radiotoxicity,jiang2012advanced,zou2018preliminary,ZOU2015114}. Therefore, the main objective of our study is to introduce a new 
fast reactivity control system based on control rods in the \gls{SD-TMSR} to control 
the reactivity during normal operation and shut down the reactor in case of 
emergency. Six different absorbing materials are 
applied to study the main neutronics and safety parameters in the SD-TMSR. We 
focus on the control rod design, absorption ability, integral and differential 
control rod worths, shutdown margin of absorbing materials, and shadowing 
effects at steady state calculation.

\v{C}erba \emph{et al.} (2017) designed a reactivity control system for the 
GFR. They utilized the MCNP5 \cite{briesmeister2000mcnptm} and KENO6 codes 
\cite{petrie1984keno} to calculate the reactivity worth and analyze the 
performance of this control system \cite{vcerba2017optimization}. Since no 
final geometry design of the control rods system is available for the SD-TMSR, 
\v{C}erba's methodology \cite{vcerba2017optimization} helped us as a starting 
point of this analysis.

@@

This paper is organized as follows: section \ref{Model-description} discusses the reactor and control rod design, section \ref{Methodology-and-tools} describes methodology and tools, section \ref{Results-and-discussion} focuses on the results and discussion, and section \ref{Conclusion} highlights the conclusions.

>>>>

The \gls{GIF} \cite{doe2002technology} determined six innovative reactor 
systems for further research and commercialization: the Very High-Temperature Reactor (VHTR), the \gls{MSR}, the 
Supercritical Water-Cooled Reactor (SWCR), the Gas-cooled Fast Reactor (GFR), 
the Sodium-cooled Fast Reactor (SFR), and the Lead-cooled Fast Reactor (LFR). 
The MSR is the only liquid-fueled reactor among these reactors. Major nuclear 
centers are pursuing MSRs with renewed interest \cite{betzler_impacts_2019, 
ashraf2020whole,betzler2016modeling,mohsin2019safety,zhang2020radiotoxicity} since
the MSR is a promising technology because of its dynamics, especially for 
thorium fuel utilization. However, this technology has difficulties in safety, 
online reprocessing, and fuel handling. Safety is one of the primary goals of 
the MSR system, and the SD-TMSR, in particular, requires further investigation to support a licensing case.
The unique characteristics of the MSR (liquid fuel, flux level, neutron economy, 
etc.) strongly affect its control system design. Doppler effect and thermal expansion of the fuel reduce
core reactivity when the core heats up, thus, graphite-moderated MSRs have 
a negative total temperature coefficient of reactivity 
\cite{ashraf2020whole,robertson_conceptual_1971,nuttin2005potential,rykhlevskii2019modeling,li_optimization_2018}.
MSR designs have drain tanks to 
hold and cool down the liquid fuel in an emergency. In most MSR design concepts, a freeze plug, which 
is located under the core, passively melts when the fuel temperature reaches a 
critical point, and drains the fuel salt from the reactor vessel to the drain 
tanks. The drain tanks have a subcritical
configuration with a large free 
surface area to readily dissipate heat by passive cooling 
\cite{elsheikh2013safety}.

At the Beginning of Life (BOL), MSRs are commonly loaded with more
fuel than that required to achieve criticality (necessary for long-term core 
operation); this leads to excess reactivity at the BOL. Recent studies on MSRs showed that this excess reactivity 
at the BOL is large for many refueling scenarios and may reach $\approx$ $8100$ $pcm$
\cite{rykhlevskii2019modeling,betzler2016modeling,ashraf2020Strategies,ashraf2018nuclear,ashraf2020whole,ashraf2019modeling}.
Additionally, during burnup, online reprocessing and refueling system helps to control the reactivity of 
the MSRs \cite{ashraf2020whole,ashraf2019Preliminary}. However, the most common and reliable procedure 
to control the reactor is to insert or withdraw control rods made of material 
with a large neutron absorption cross section (e.g., boron, cadmium) 
\cite{duderstadt650nuclear}. 
Insertion of control rods introduces negative reactivity into the 
core which helps to compensate the excess reactivity and 
adjust the power level of the core or shut down the reactor in case of 
emergency \cite{glasstone1967nuclear}. Therefore, we should estimate 
the reactivity worth of the control rods 
\cite{varvayanni2009estimation,fadaei2009control,aoyama2007core,bretscher1997computing}.
 The reactivity worth of control rods correlates with the interference 
(shadowing effects) between control rod clusters 
\cite{girardin2008development,vcerba2017optimization}. 
The control rod worth and its efficiency to absorb excess positive reactivity is a subject of major interest since it directly affects reactor safety \cite{liu2018criticality,atkinson2019small,vcerba2017optimization,do2019criticality,guo2019advanced,varvayanni2009estimation}.

Boron carbide (B$_4$C) is a commonly used material for the control rods 
\cite{zhong2019preliminary,steinbruck2010degradation,dunner1984absorber}; 
however, we may need to enrich the boron isotope ($^{10}$B) to reach 
the necessary absorption cross section. Additionally, issues related to helium gas release through (n,$\alpha$) reactions of $^{10}$B, high loss of the absorption ability under irradiation, and swelling limit the B$_4$C lifespan 
\cite{guo2019optimized}. Guo (2019), Gosset (2017), and Rudy (2011) summarized the properties of the 
potential alternative absorbers for Generation-IV reactors such as 
hafnium-based materials and rare earth oxides. These absorbers have 
high thermal conductivity, good resistance to neutron irradiation, and
absorb neutrons mainly through (n,$\gamma$) reactions
\cite{guo2019optimized,gosset2017absorber,konings2011comprehensive}.

The SD-TMSR with a thermal power of 2,250 MW$_{th}$ 
\cite{ashraf2020whole,li_optimization_2018} is a graphite-moderated 
molten salt reactor. Adjusting fertile and fissile feed rates helps to control the reactivity of 
the SD-TMSR \cite{ashraf2020whole,ashraf2020Strategies,li_optimization_2018}. However, a reactivity control system for maneuvering and emergency shutdown in the SD-TMSR has not been introduced in the literature \cite{li_optimization_2018,zou2018transition,zhang2020radiotoxicity,jiang2012advanced,zou2018preliminary,ZOU2015114}. Therefore, the main objective of our study is to introduce a new, 
rapid reactivity control system based on control rods in the SD-TMSR to control 
the reactivity during normal operation and shut down the reactor in case of 
emergency. Six absorbing material options are considered in the context of the 
neutronics and safety parameters in the SD-TMSR. We 
focus on control rod design, absorption ability, integral and differential 
control rod worths, shutdown margin, and shadowing 
effects at steady state calculation.

Xuemei \emph{et al.} (2013) calculated the control worth in the thorium molten salt
reactor by using MCNP5 \cite{briesmeister2000mcnptm}. We adopted the SD-TMSR
core geometry optimized by Li \emph{et al.} \cite{li_optimization_2018} which
is different from the Molten Salt Breeder Reactor-like geometry by Mathieu \emph{et al.}
\cite{mathieu2006thorium} adopted by Xuemei \emph{et al.} \cite{xuemei2013study}.
Additionally, Xuemei \emph{et al.} studied the natural B$_4$C as absorbing material
while we considered six different absorbing materials.

\v{C}erba \emph{et al.} (2017) designed a reactivity control system for the 
GFR. They utilized the MCNP5 and KENO6 codes 
\cite{petrie1984keno} to calculate the reactivity worth and analyze the 
performance of this control system \cite{vcerba2017optimization}. Since no
geometry design of the control rods system is available for the SD-TMSR, 
\v{C}erba's methodology \cite{vcerba2017optimization} helped us as a starting 
point of this analysis.

@@

This paper is organized as follows: section \ref{Model-description} discusses the reactor and control rod design, section \ref{Methodology-and-tools} describes methodology and tools adopted to evaluate the control rod design, section \ref{Results-and-discussion} focuses on the results and discussion, and section \ref{Conclusion} highlights the conclusions.

### 2020-03-24 paper/methods.tex
after Prof. Huff's comments

The Chinese Academy of Sciences proposed the Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) design in 2011
\cite{li_optimization_2018,jiang2012advanced,li2015analysis,li2017model}. The 
\gls{SD-TMSR} is a graphite-moderated molten salt reactor with a thermal power 
of 2,250 MW$_{th}$. The design of the \gls{SD-TMSR} is inspired by the 
\gls{MSBR} \cite{robertson_conceptual_1971} and the \gls{TMSR} 
\cite{nuttin2005potential} after modifying the geometry to control the 
positive moderator temperature coefficient in the MSBR. Li \emph{et al.} and Ashraf \emph{et al.}
described in detail the \gls{SD-TMSR} core geometry
\cite{li_optimization_2018,ashraf2020whole}. The core of the 
\gls{SD-TMSR} is a right cylinder divided into the inner zone (486 fuel tubes) 
and the outer zone (522 fuel tubes) to enhance breeding performance.

In this study, the fuel salt composition is 70LiF - 17.5BeF$_2$ - 
12.5(HM)F$_N$ mole\%, where HM is the heavy metal (i.e. $^{232}$Th and fissile 
materials), and $N$ depends on the chosen fissile material and the 
thermochemical state of the liquid fuel salt. Three different types of initial 
fissile materials are considered: (1) $^{233}$U \cite{ashraf2020whole}, 
(2) reactor-grade Pu \cite{marka1993explosive}, and (3) transuranic (TRU) 
elements from \gls{LWR} \gls{SNF} \cite{de2000scenarios}.
The density and volume of the fuel salt are 3.3 g/cm$^{3}$ and 52.9 m$^3$, 
respectively. The liquid fuel salt circulates continuously through the fuel 
tubes that pierce the graphite hexagonal prisms. The core is surrounded by 
axial and radial graphite reflectors to minimize the neutron leakage.
A 10-cm-thick B$_4$C cylinder surrounds the core to shield against neutrons and heat.
Finally, the \gls{SD-TMSR} pressure vessel holds all reactor components and is made of 
a Hastelloy N alloy. The main characteristics of the \gls{SD-TMSR} are 
summarized in Table~\ref{tab:table1}.

\begin{table}  %[!ht]
	\caption{The main characteristics of the SD-TMSR \cite{li_optimization_2018,ashraf2020whole}.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{l | r}
		\hline
		Thermal power, MW$_{th}$          				&  2,250  \\ 
		Fuel salt components                            & LiF-BeF$_2$-(\gls{HM})F$_N$ \\
		Fuel composition, mole\%                        & 70-17.5-12.5    \\
		$^7$Li enrichment, \%        				& 99.995   \\
		Fuel temperature, K 							& 900  \\
		Fuel density at 900 K, g/cm$^3$		  		& 3.3 \\
		Fuel dilatation coefficient, g/(cm$^3$$.$K)  &  -6.7$\times$10$^{-4}$ \\
		Graphite density, g/cm$^3$             	    & 2.3	\\ 
		B$_4$C density, g/cm$^3$					& 2.52  \\ 
		Core diameter, cm								& 460  \\
		Core height, cm									& 460  \\
		Side length of the graphite hexagonal prism, cm   & 7.5 \\
		Inner radius, cm							& 3.5  \\
		Outer radius, cm							& 5  \\
		Ratio of molten salt and graphite in the inner zone	&  0.357  \\
		Ratio of molten salt and graphite in the outer zone &  1.162  \\
		Fuel volume, m$^3$  &	52.9 \\
		\hline
	\end{tabularx}
	\label{tab:table1}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The reactivity of the SD-TMSR core is controlled by two clusters of control 
rods:
\begin{enumerate}
\item Control Safety Devices (CSD);
\item Shutdown Safety Devices (SSD).
\end{enumerate}
The CSD system is designed for reactivity control during normal operation and the SSD system is designed for an emergency reactor shutdown.
In the present work, six different absorbing materials are considered based on their neutronics and safety performance:
\begin{enumerate}
\item natural B$_4$C (19.9\% $^{10}$B);
\item B$_4$C with boron enriched to 90\% $^{10}$B;
\item hafnium diboride (HfB$_2$);
\item hafnium hydride (HfH$_{1.62}$);
\item gadolinium oxide (Gd$_2$O$_3$);
\item europium oxide (Eu$_2$O$_3$).
\end{enumerate}

The control rod is a cylinder with a radius of 0.75 cm and a height of 520 cm. 
The absorbing material is surrounded by a 0.25-cm-thick cladding made of AIM1 
(15Cr-15Ni) steel alloy \cite{SERAN2017285} and the guide tube is made of 
SiC structural material (see Figure~\ref{fig:cr}). We simulated a small gap between the 
cladding and guide tube to facilitate the control rod movement.

Since the total number and distribution of the control assemblies in the SD-TMSR are unknown, we proposed an original distribution as a starting point of this analysis. We added clusters consisting of four control rods to specific graphite hexagonal prisms (elements) in the SD-TMSR core. Every four control rods (cluster) can move together as one group. Figures~\ref{fig:graphite_elemen} and~\ref{fig:graphite_elemen1} demonstrate the plan and axial view of the graphite element with the control rods. The total number of graphite elements with control rods are 25: 16 CSD and 9 SSD.
\begin{figure}[t!]  % replace 't' with 'b' to \centering
	\centering
	\hspace{+0.65in} 
	\includegraphics[width=\textwidth]{cr.png}
	\caption{Cross section of the B$_4$C control rod.}
	\label{fig:cr}
\end{figure}
\begin{figure}[t!]  % replace 't' with 'b' to \centering
	\centering
	\hspace{+0.65in}
	\includegraphics[width=\textwidth]{graphite_element.png}
	\caption{$XY$ section of graphite element with the four control rods 
	(cluster) located at the same distance from the fuel channel.}
	\label{fig:graphite_elemen}
\end{figure}
\begin{figure}[t!]  % replace 't' with 'b' to \centering
	\centering
	\hspace{+0.65in}
	\includegraphics[width=\textwidth]{graphite_element1.png}
	\caption{$XZ$ section of graphite element with control rods.}
	\label{fig:graphite_elemen1}
\end{figure}

Figure~\ref{fig:core_25} illustrates the numbering scheme of control rod 
clusters in the SD-TMSR core.
The CSD1-16 clusters are represented as yellow and distributed as two rings: inner and outer (peripheral) ring. The inner ring includes CSD from 1 to 6, while the outer ring includes CSD from 7 to 16. Red stands for SSD1-9 clusters.
We distributed the graphite elements with control rod clusters uniformly in 
the inner core of the SD-TMSR, in which the moderator-to-fuel ratio is high.
The selected core segment at the upper left corner of 
Figure~\ref{fig:core_25} shows that both CSD and SSD clusters consist of four 
control rods located at the same distance from the fuel channel center.
\begin{figure}[t!]  % replace 't' with 'b' to \centering
	\centering
	\hspace{+0.65in}
	\includegraphics[width=\textwidth]{core_25.png}
	\caption{Distribution of the graphite elements with CRs in the SD-TMSR core. Green - fuel salt, blue - graphite, pink - B$_4$C, and light-green - vessel (H-alloy).}
	\label{fig:core_25}
\end{figure}

\section{Methodology and tools} \label{Methodology-and-tools}
\subsection{Control rod design evaluation}
In this work, SERPENT-2 \cite{leppanen2014serpent} is used to 
perform steady state calculations for the full core of the SD-TMSR with 
the suggested control rod design. We adopted the ENDF-VII.0 cross section library 
for all calculations in the present work. The results demonstrate whole-core 
runs of $50,000$ neutrons per cycle, for 50 inactive and 500 active cycles. The 
statistical error in $k_{eff}$ from the SERPENT-2 output is $\leq$ $25$ 
$pcm$.

@@

Interference between control rods (CRs) or shadowing effects occur when one 
(or more) control rod affects the reactivity worth of another control rod in 
the surroundings. Thus, the shadowing effect appears when the combined rod worth
is less than the sum of the individual worths. Oppositely, anti-shadowing is observed 
when the combined rod worth is greater than the sum of the individual worths.
The core height-to-diameter ratio (H/D) and the three-dimensional configuration 
of the CRs affect the degree of the interference between CRs \cite{girardin2007control}.

The amplification factor (A$_{CRi}$) of the i$^{th}$ CR helps to evaluate the shadowing effects between CR clusters. The A$_{CRi}$ is calculated by equation~\ref{Equ:3} \cite{girardin2007control,vcerba2017optimization}, where $\Delta\rho$$_{CR(1,2,\ldots N)}$ is the total worth of all CRs (from $1$ to $N$), $\Delta\rho$$_{CR(1,2,\ldots N-i)}$ is the total worth of all CRs except the i$^{th}$ rod, and $\Delta\rho$$_{CRi}$ is the worth of the i$^{th}$ rod:

@@

If A$_{CRi}$ is $<$1, the CRW is reduced due to shadowing effects, but if A$_{CRi}$ is $>$1 the CRW is amplified and anti-shadowing effects occur. A$_{CRi}$ = 1 means no shadowing effects occur.

@@

The integral CRW is the total reactivity change due to the full 
insertion or withdrawal of the CR. However, the differential CRW is the amount of 
reactivity inserted per unit of withdrawal [\$/cm]. To calculate those 
parameters, we varied the position of CR clusters from fully withdrawn to 
fully inserted. Equation~\ref{Equ:4} is used to calculate the integral CRW 
[\$], where $k_{j}$ and $k_{j-1}$ are the effective multiplication factor 
after and before CR insertion to the $j$$^{th}$ step, respectively, $\beta_{j}$ is the effective 
fraction of delayed neutrons at the $j$$^{th}$ step, and $N$ is the number of steps:

@@

Equation~\ref{Equ:5} is used to calculate the differential CRW, where 
$Z$ is the coordinate of the bottom of the control rod:

>>>>

The Chinese Academy of Sciences proposed the SD-TMSR design in 2011
\cite{li_optimization_2018,jiang2012advanced,li2015analysis,li2017model}. The 
SD-TMSR is a graphite-moderated molten salt reactor with a thermal power 
of 2,250 MW$_{th}$. The design of the SD-TMSR is inspired by the 
\gls{MSBR} \cite{robertson_conceptual_1971} and the \gls{TMSR} 
\cite{nuttin2005potential} after modifying the geometry to control the 
positive moderator temperature coefficient in the MSBR. Li \emph{et al.} and Ashraf \emph{et al.}
described in detail the SD-TMSR core geometry
\cite{li_optimization_2018,ashraf2020whole}. The core of the 
SD-TMSR is a right cylinder divided into an inner zone (486 fuel tubes) 
and an outer zone (522 fuel tubes) to enhance breeding performance.

In this study, the fuel salt composition is LiF-BeF$_2$-(HM)F$_N$ (70-17.5-12.5 mol\%),
where HM is the heavy metal (i.e. $^{232}$Th and fissile 
materials), and $N$ depends on the chosen fissile material and the 
thermochemical state of the liquid fuel salt. Three different types of initial 
fissile materials are considered: (1) $^{233}$U \cite{ashraf2020whole}, 
(2) reactor-grade Pu \cite{marka1993explosive}, and (3) transuranic (TRU) 
elements from \gls{LWR} \gls{SNF} \cite{de2000scenarios}.
The density and volume of the fuel salt are 3.3 g/cm$^{3}$ and 52.9 m$^3$, 
respectively. The liquid fuel salt circulates continuously through the channels
that pierce the graphite hexagonal prisms. The core is surrounded by 
axial and radial graphite reflectors to minimize the neutron leakage.
A 10-cm-thick B$_4$C cylinder surrounds the core to shield against neutrons and heat.
Finally, the SD-TMSR pressure vessel holds all reactor components and is made of 
a Hastelloy N alloy. The main characteristics of the SD-TMSR are 
summarized in Table~\ref{tab:table1}.

\begin{table}  %[!ht]
	\caption{The main characteristics of the SD-TMSR \cite{li_optimization_2018,ashraf2020whole}.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{l | r}
		\hline
		Thermal power, MW$_{th}$          				&  2,250  \\ 
		Fuel salt components                            & LiF-BeF$_2$-(\gls{HM})F$_N$ \\
		Fuel composition, mole\%                        & 70-17.5-12.5    \\
		$^7$Li enrichment, \%        				& 99.995   \\
		Fuel temperature, K 							& 900  \\
		Fuel density at 900 K, g/cm$^3$		  		& 3.3 \\
		Dilatation coefficient, g/(cm$^3$$\cdot{}$K)  &  -6.7$\times$10$^{-4}$ \\
		Graphite density, g/cm$^3$             	    & 2.3	\\  
		Core diameter, cm								& 460  \\
		Core height, cm									& 460  \\
		Side length of the graphite hexagonal prism, cm   & 7.5 \\
		Inner radius, cm							& 3.5  \\
		Outer radius, cm							& 5  \\
		Volume ratio of molten salt to graphite \\in the inner zone	&  0.357  \\
		Volume ratio of molten salt to graphite \\in the outer zone &  1.162  \\
		Fuel volume, m$^3$  &	52.9 \\
		B$_4$C density, g/cm$^3$  &  2.54 \\
		HfB$_2$ density, g/cm$^3$  &  10.5 \\
		HfH$_{1.62}$ density, g/cm$^3$ &  11.4 \\
		Gd$_2$O$_3$ density, g/cm$^3$  &  7.04 \\
		Eu$_2$O$_3$ density, g/cm$^3$  &  7.38 \\
		SiC density, g/cm$^3$  & 3.21 \\
		AIM1 cladding density, g/cm$^3$  & 7.987 \\
		\hline
	\end{tabularx}
	\label{tab:table1}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The present paper proposes two sets of rods to control the reactivity of the SD-TMSR core:
\begin{enumerate}
\item Control Safety Devices (CSD);
\item Shutdown Safety Devices (SSD).
\end{enumerate}
The CSD system is designed for reactivity control during normal operation and the SSD system is designed for an emergency reactor shutdown.
In the present work, six different absorbing materials are considered based on their neutronics and safety performance:
\begin{enumerate}
\item natural B$_4$C (19.9\% $^{10}$B);
\item B$_4$C (enriched to 90\% $^{10}$B);
\item hafnium diboride (HfB$_2$);
\item hafnium hydride (HfH$_{1.62}$);
\item gadolinium oxide (Gd$_2$O$_3$);
\item europium oxide (Eu$_2$O$_3$).
\end{enumerate}

The control rod is a cylinder with a radius of 0.75 cm and a height of 520 cm. 
The absorbing material is surrounded by a 0.25-cm-thick cladding made of AIM1 
(15Cr-15Ni) steel alloy \cite{SERAN2017285} and the guide tube is made of 
SiC structural material (see Figure~\ref{fig:cr}). We simulated a 0.04-cm-thick gap between the 
cladding and guide tube to facilitate the control rod movement.
All densities of rod materials are listed in
Table~\ref{tab:table1}.

\begin{figure}[b!]  % replace 't' with 'b' to \centering
	\centering
	\hspace{+0.65in} 
	\includegraphics[width=\textwidth]{cr.png}
	\caption{Cross section of the B$_4$C control rod.}
	\label{fig:cr}
\end{figure}

Since the total number and distribution of the control assemblies in the SD-TMSR have not been determined, we propose an original distribution as a starting point of this analysis. We added clusters consisting of four control rods to specific graphite hexagonal prisms (elements) in the SD-TMSR core. Every four control rods can move together as one group (cluster). Figures~\ref{fig:graphite_elemen} and~\ref{fig:graphite_elemen1} demonstrate the plan and axial view of the graphite element with the control rods. We propose 25 graphite elements with control rods: 16 Control Safety Devices (CSD) and 9 Shutdown Safety Devices (SSD).

\begin{figure}[t!]  % replace 't' with 'b' to \centering
	\centering
	\hspace{+0.65in}
	\includegraphics[width=\textwidth]{graphite_element.png}
	\caption{$XY$ section of graphite element with the four control rods 
	(cluster) located at the same distance from the fuel channel.}
	\label{fig:graphite_elemen}
\end{figure}
\begin{figure}[t!]  % replace 't' with 'b' to \centering
	\centering
	\hspace{+0.65in}
	\includegraphics[width=\textwidth]{graphite_element1.png}
	\caption{$XZ$ section of graphite element with control rods.}
	\label{fig:graphite_elemen1}
\end{figure}

Figure~\ref{fig:core_25} illustrates the numbering scheme of control rod 
clusters in the SD-TMSR core.
The CSD1-16 clusters are represented as yellow and distributed as two rings: inner and outer (peripheral) ring. The inner ring includes CSD from 1 to 6, while the outer ring includes CSD from 7 to 16. Red stands for SSD1-9 clusters.
We distributed the graphite elements with control rod clusters uniformly in 
the inner core of the SD-TMSR, in which the moderator-to-fuel ratio is high.
The selected core segment at the upper left corner of 
Figure~\ref{fig:core_25} shows that both CSD and SSD clusters consist of four 
control rods located at the same distance from the fuel channel center.
\begin{figure}[t!]  % replace 't' with 'b' to \centering
	\centering
	\hspace{+0.65in}
	\includegraphics[width=\textwidth]{core_25.png}
	\caption{Distribution of the graphite elements with CRs in the SD-TMSR core.}
	\label{fig:core_25}
\end{figure}

\section{Methodology and tools} \label{Methodology-and-tools}
\subsection{Control rod design evaluation}
In this work, SERPENT-2 \cite{leppanen2014serpent} is used to 
perform steady state calculations for the full core of the SD-TMSR with 
the suggested control rod design. We adopted the ENDF-VII.0 cross section library 
for all calculations in the present work. The results demonstrate whole-core 
runs of $50,000$ neutrons per cycle, for 50 inactive and 500 active cycles, and
statistical error in $k_{eff}$ of $\leq$ $25$ 
$pcm$.

@@

Interference between control rods (CRs) or shadowing effects occur when one 
(or more) control rod impacts the reactivity worth of another control rod in 
the surroundings. Thus, the shadowing effect appears when the combined rod worth
is less than the sum of the individual worths. Meanwhile, anti-shadowing is observed 
when the combined rod worth is greater than the sum of the individual worths.
The core height-to-diameter ratio (H/D) and the three-dimensional configuration 
of the CRs affect the degree of the interference between CRs \cite{girardin2007control}.

The amplification factor of the i$^{th}$ CR (A$_{CRi}$) helps to evaluate the shadowing effects between CR clusters. The A$_{CRi}$ is calculated by equation~\ref{Equ:3} \cite{girardin2007control,vcerba2017optimization}, where $\Delta\rho$$_{CR(1,2,\ldots N)}$ is the total worth of all CRs (from $1$ to $N$), $\Delta\rho$$_{CR(1,2,\ldots N-i)}$ is the total worth of all CRs except the i$^{th}$ rod, and $\Delta\rho$$_{CRi}$ is the worth of the i$^{th}$ rod:

@@

If A$_{CRi}$ is $<$1, the CRW is reduced due to shadowing effects, but if A$_{CRi}$ is $>$1, the CRW is amplified and anti-shadowing effects occur. A$_{CRi}$ = 1 means no shadowing effects occur.

@@

The integral CRW is the total reactivity change due to the full 
insertion or withdrawal of the CR. However, the \textit{differential CRW} is the
reactivity inserted per unit of withdrawal [\$/cm]. To calculate those 
parameters, we varied the position of CR clusters from fully withdrawn to 
fully inserted. Equation~\ref{Equ:4} is used to calculate the integral CRW 
[\$], where $k_{j-1}$ and $k_{j}$ are the effective multiplication factors 
before and after CR insertion to the $j$$^{th}$ step, respectively, $\beta_{j}$ is the
fraction of delayed neutrons at the $j$$^{th}$ step, and $N$ is the number of steps:

@@

Equation~\ref{Equ:5} is used to calculate the differential CRW, where 
$\Delta Z$ is the length of rod inserted:
